`flippant` --- An `R` package for the automated analysis of fluorescence--based

### 2016-12-16 inst/manuscript/manuscript.rmd
Rework 'Declarations' section to conform to editorial policy and in response to reviewer;

## Consent for publication
Not applicable.

## Availability of data and material
Upon acceptance of the manuscript, `flippant` will be deposited as a
self--contained `R` package including all data presented in the `Bioconductor`
collection of tools for biomedical data analysis [@huber_orchestrating_2015].

@@

>>>>

## Consent to publish
Not applicable.

## Availability of data and materials
The `R` package `flippant` provides all functionality as well as data presented
here along with extensive additional documentation and example code accessible
from within `R` in an integrated manner.

The package is available as an `R` source package in the version current at
acceptance for publication in the supplementary material and may be installed
from that file using ` install.packages(file.choose(), type = 'source')`.

The package is also uploaded to the comprehensive `R` archive network (CRAN) and
may thus be installed in its most up--to date version using 
`install.packages('flippant')` from within any appropriately configured `R`
installation.

Thirdly the code base and development history is publicly accessible at \
`https://bitbucket.org/graumannlabtools/flippant`.

@@

## Acknowledgements
Not applicable.
